### 2019-02-12 2-Chapters/1-Chapter/chapter1.tex
Okay for outline

% ----------------------------------------------------------------------------
\section{List of publications}
\label{sec:1:contributions}

>>>>

% ----------------------------------------------------------------------------
\section{Organization of the thesis}
\label{sec:1:organization}

Here we discuss quickly the organization of the thesis.

\begin{figure}[h!]
    \centering
    \resizebox{0.80\textwidth}{!}{
    \begin{tikzpicture}[>=latex',line join=bevel,scale=3]
        %
        \node[align=center] (introduction) at (0,2.5) [square,draw] {Chapter~\ref{chapter:1}\\Introduction};
        \node[align=center] (chapter2) at (0,2) [square,draw] {Chapter~\ref{chapter:2}\\Multi-Armed Bandit models};
        \node[align=center] (chapter3) at (4,2) [square,draw] {Chapter~\ref{chapter:3}\\SMPyBandits: simulation\\library for MAB};
        \node[align=center] (chapter4) at (-2,1) [square,draw] {Chapter~\ref{chapter:4}\\Two MAB models for IoT networks};
        \node[align=center] (chapter5) at (0,1) [square,draw] {Chapter~\ref{chapter:5}\\Multi-players MAB};
        \node[align=center] (chapter6) at (2,1) [square,draw] {Chapter~\ref{chapter:6}\\Non-stationary MAB models};
        \node[align=center] (conclusion) at (0,0) [square,draw] {Chapter~\ref{chapter:conclusion}\\General conclusion};
        %
        \draw [color=black,thick,->] (introduction) to (chapter2);
        \draw [color=black,thick,<->] (chapter2) to (chapter3);
        \draw [color=black,thick,->] (chapter2) to (chapter4);
        \draw [color=black,thick,->] (chapter2) to (chapter5);
        \draw [color=black,thick,->] (chapter2) to (chapter6);
        \draw [color=black,thick,->] (chapter4) to (conclusion);
        \draw [color=black,thick,->] (chapter5) to (conclusion);
        \draw [color=black,thick,->] (chapter6) to (conclusion);
        %
    \end{tikzpicture}
    }
    \caption{Organization of the thesis.}
    \label{fig:1:organization}
\end{figure}

% ----------------------------------------------------------------------------
\section{List of publications}
\label{sec:1:listPublications}
